FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-05-11 ess_marmo.tex
Finalizing comments.

\begin{table}
\caption{Codes to be used in CTYPE FITS keyword in order to identify the planetary body.
Codes for planets are assumed in \citet{calagreisenI}.
We propose to add codes for classes of targets,
more or less corresponding to PDS4 Target type attribute and to EPN-TAP
target\_class parameter.}
\centering
\begin{tabular}{l l}
\hline
Body & CTYPE$^{a}$ \\ 
\hline
Moon & SE \\
Mercury & ME \\
Venus & VE \\
Mars & MA \\
Jupiter & JU \\
Saturn & SA \\
Uranus & UR \\
Neptune & NE \\
Satellites (other than the Moon) & ST \\
Asteroids$^{b}$ & AS \\
Dwarf Planets & DW \\
Comets & CO \\
\hline
\multicolumn{2}{l}{$^{a}$From \citet{calagreisenI}} \\
\multicolumn{2}{l}{$^{b}$Transneptunian (TNO) and Kuiper Belt (KBO) objects must be placed there}
\end{tabular}
\label{table:ctype}
\end{table}

@@

\item{\texttt{ORIGIN}.
It contains string identifying the organization or institution responsible for
creating the FITS file.}

>>>>

\begin{table}
\caption{Codes to be used in CTYPE FITS keyword in order to identify the planetary body.
Codes for planets are implied in \citet{calagreisenI}.
We propose to add codes for classes of targets,
more or less corresponding to PDS4 Target type attribute and to EPN-TAP
target\_class parameter.}
\centering
\begin{tabular}{l l}
\hline
Body & CTYPE$^{a}$ \\ 
\hline
Moon & SE \\
Mercury & ME \\
Venus & VE \\
Mars & MA \\
Jupiter & JU \\
Saturn & SA \\
Uranus & UR \\
Neptune & NE \\
Satellites (other than the Moon) & ST \\
Asteroids$^{b}$ & AS \\
Dwarf Planets & DW \\
Comets & CO \\
\hline
\multicolumn{2}{l}{$^{a}$From \citet{calagreisenI}} \\
\multicolumn{2}{l}{$^{b}$Transneptunian (TNO) and Kuiper Belt (KBO) objects must be placed there}
\end{tabular}
\label{table:ctype}
\end{table}

@@

\item{\texttt{ORIGIN}.
It contains string identifying the organization or institution responsible for
creating the FITS file.
No clear correspondence for this reserved FITS keyword is available in PDS4.
This is because PDS4 is focused on referencing the authors of the data collection
and its metadata curation, not the data producer itself.
Yet, the content of the \texttt{ORIGIN} keyword can be inserted in a PDS4 comment.}
